A Switching Planner for Combined Task and Observation Planning

### 2011-03-09 subarchitectures/planner.sa/trunk/src/latex/IJCAI-Workshop/conc.tex
New versions

We have addressed a key challenge, specifically that of high-level
continual planning and execution monitoring for efficient
deliberations according to rich probabilistic models afforded by
recent integrated robotic systems. We developed a system that can plan
quickly given large realistic probabilistic models, by switching
between: (a) fast sequential planning, and (b) expensive DT planning
in small abstractions of the problem at hand. Sequential and DT
planning is interleaved, the former identifying a rewarding sequential
plan in the underlying process, and the latter solving small sensing
problems posed during sequential plan execution.
%%
We have evaluated our system in large real-world task and
observation planning problems, finding that it performs quickly
and relatively efficiently.

>>>>

We have addressed a key challenge, specifically that of high-level
continual planning for efficient deliberations according to rich
probabilistic models afforded by recent integrated robotic systems. We
developed a system that can plan quickly given large realistic
probabilistic models, by switching between: (a) fast sequential
planning, and (b) expensive DT planning in small abstractions of the
problem at hand. Sequential and DT planning is interleaved, the former
identifying a rewarding sequential plan for the underlying process, and
the latter solving small sensing problems posed during sequential plan
execution.
%%
We have evaluated our system in large real-world task and
observation planning problems, finding that it performs quickly
and relatively efficiently.

### 2011-03-09 subarchitectures/planner.sa/trunk/src/latex/IJCAI-Workshop/ijcai-workshop.tex
New versions

@@

\bibliographystyle{aaai}
\bibliography{papers}

>>>>

\title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}
\setcounter{secnumdepth}{0}

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to promote efficient
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small abstract subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We evaluate our approach
in large problems from a realistic robot exploration domain.

%% \section{Propositional Decision-Theoretic Planning}
%% \input{prop-dtp.tex}

\section{Planning Language and Notations}
\input{dtpddl.tex}

\bibliographystyle{named}
\bibliography{papers}

@@

\bibliographystyle{named}
\bibliography{papers}
